Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-30 sections/approach.tex
edit text

Our goal is to improve the efficiency and confidence in determining the usefulness of review comments.
We define a \emph{useful} comment as one that contributes to improving the proposed changes and a \emph{useless}\footnote{Although we call these comments \emph{useless}, it might be useful---or sometimes even required---in some other context, such as to facilitate communication.} comment as one that does not.
Usefulness is not dichotomous and hence we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential.
Therefore, our approach is largely based on relevance the comment has to the proposed change (as documented within a MCR system).
A primary factor in relevance is similarly, and so it is natural for us to consider classification using \emph{similarity conditions}\cite{Davies2012}. 
%\dan{can we find a reference for relevance and similarly?}
We assume that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful.
Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity}, the less relevant, and hence less useful.

\subsection{Approach}
Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification.
That is, for some degree of similarity a comment is most likely useful, and for some degree of dissimilarity it is most likely not useful.
The key is determining these degrees in a practical and effective manner.
%\textbf{Approach Overview.} 
Fig. \ref{fig:overview} shows an overview of our proposed classification approach.
Usefulness of a comment is determined by computing its semantic similarity with the commit message of its proposed change and observing if it satisfies \emph{usefulness classification likelihood conditions}.
The conditions are simply threshold values of similarity and dissimilarity empirically determined to optimize a desired likelihood objectives.

@@

% again, I can't see Fig. \ref{fig:overview}(a)
% Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
We calculate semantic similarity using the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language\cite{did}; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously\cite{dfdf}.
%For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig. \ref{fig:overview}(b). \thai{The %overview figure does not have (a) and (b)...}
%\dan{what was the actual effort (in person-hours) to create the training data?}

Our training data is a small set of randomly-selected pairs of comments and the corresponding commit messages.
These comments are manually assessed for usefulness.
%Each comment is assessed by three different people independently.
%For each \texttt{YES} vote, a single point is given to that comment.
%This means that a comment will receive a score of 0, 1, 2, or 3.
For statistical purposes, at least 30 useful and 30 useless comments must be collected.
The similarity and dissimilarity metrics are then computed for the data set.
These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that best discriminate useful comments and $S'_T$ and $D'_T$ for useless comments. 
%Other likelihood functions could be used depending on precision, recall, or risk goals.
We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure,
which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
In this study, we used the F$_1$-measure, which equally prioritize precision and recall.
Different weighting can be used by different F$_\beta$ measures depending on an application.

\subsection{Usefulness Classification Conditions} 
Using those thresholds, we can classify the usefulness of comments for the rest of comments (as test data) in review history according to the classification model as follows: given a comment $c$ and a corresponding commit message $m$,
\begin{itemize}
\item \textbf{useful}: $\Theta(c,m,S_T,D_T) = \True$ iff $\Sim(m,c) \geq S_T$ and $\Dist(m,c) \leq D_T$.
\item \textbf{useless}: $\Omega(c,m,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
\item \textbf{undetermined}: neither or both of the above conditions are $\True$.
% We also refer to them as \emph{neither} and \emph{overlap}.
\end{itemize}

The functions $\Sim(m,c)$ and $\Dist(m,c)$ are the similarity and dissimilarity measures relative to the proposed change commit message $m$ for the text of comment $c$ using cosine similarity and euclidian distance respectively.
Two metrics are used because they are independently generated and thus provides better discrimination for classification.
We also found experimentally that using two metrics has higher performance than just one.

@@

>>>>

\textbf{Definition:} We define a \emph{useful} comment as one that contributes to improving the proposed change, and a \emph{useless}\footnote{Although we call these comments \emph{useless} in our study, it might actually be useful---or sometimes even required---in some other contexts, such as to facilitate communication or to enforce guidelines.} comment as one that does not.

Our goal is to improve the efficiency and confidence in determining the usefulness of review comments.
Usefulness is not dichotomous and hence we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential.
Therefore, our approach is largely based on relevance the comment has to the proposed change (as documented within a MCR system).
A primary factor in relevance is similarly, and so it is natural for us to consider classification using \emph{similarity conditions}\cite{Davies2012}. 
%\dan{can we find a reference for relevance and similarly?}
We assume that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful.
Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity}, the less relevant, and hence less useful.

Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification.
That is, for some degree of similarity a comment is most likely useful, and for some degree of dissimilarity it is most likely useless.
The key is to determine these degrees in a practical and effective manner.

@@

%\textbf{Approach Overview.} 
Fig. \ref{fig:overview} shows an overview of our proposed classification approach.
Usefulness of a comment is determined by computing its semantic similarity with the commit message of its proposed change and observing if it satisfies \emph{usefulness classification likelihood conditions}.
The conditions are simply threshold values of similarity and dissimilarity empirically determined to optimize a desired likelihood objectives.
In our case example we chose to maximize the F-measure, but other likelihood functions could be used depending on precision, recall, or risk goals.

% again, I can't see Fig. \ref{fig:overview}(a)
% Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
To calculate semantic similarity, we used the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language\cite{did}; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously\cite{dfdf}.
%For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig. \ref{fig:overview}(b). \thai{The %overview figure does not have (a) and (b)...}
%\dan{what was the actual effort (in person-hours) to create the training data?}

Our training data is a small set of randomly-selected pairs of comments and the corresponding commit messages.
These comments are manually assessed for usefulness.
%Each comment is assessed by three different people independently.
%For each \texttt{YES} vote, a single point is given to that comment.
%This means that a comment will receive a score of 0, 1, 2, or 3.
For statistical purposes, at least 30 useful and 30 useless comments must be collected.
The similarity and dissimilarity metrics are then computed for the data set.
These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments.

%\textbf{Usefulness Classification Conditions.} 
Using those thresholds, we can classify the usefulness of comments for the rest of comments (as test data) in review history according to the classification model as follows: given a comment $c$ and a corresponding commit message $m$,
\begin{itemize}
\item \textbf{useful}: $\Theta(c,m,S_T,D_T) = \True$ iff $\Sim(m,c) \geq S_T$ and $\Dist(m,c) \leq D_T$.
\item \textbf{useless}: $\Omega(c,m,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
\item \textbf{undetermined}: neither or both of the above conditions are $\True$.
% We also refer to them as \emph{neither} and \emph{overlap}.
\end{itemize}

The functions $\Sim(m,c)$ and $\Dist(m,c)$ are the similarity and dissimilarity measures relative to the proposed change commit message $m$ for the text of comment $c$ using cosine similarity and euclidian distance, respectively.
Two metrics are used because they are independently generated and thus provides better discrimination for classification.
We also found experimentally that using two metrics has higher performance than just one.

@@

We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that maximize the F-measure,
which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
In this paper, we used the F$_1$ measure, which gives equal weight to both precision and recall.
Depending on application, different weights can be given by choosing a different F$_\beta$ measure.

### 2014-07-30 sections/results.tex
edit text

\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignored all messages that automatically generated.
%In Gerrit, the comment history is composed of human-written comments from reviewers and automatically generated messages.
These automatic messages are generated by Gerrit, continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities. For example, \textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'}. In practice, they are not considered in code review  and are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.

To do so, we first ignore all comments written by bots i.e. \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}. Second, we removed message including reviewers comments by finding common patterns frequently occurred using regular expression. This would leave us only human-written comments that will be used in further preprocessing.

@@

\subsection{Manual Comment Usefulness Assessment}
In this case study, three participants (the first two authors and one student) independently classify comments by giving a question, ``does this comment technically contribute to its change or not?''
Then, the participants gave a vote for \texttt{YES} if the comment is likely to be useful and \texttt{NO} otherwise.
From the voting scores, we regarded that the comments with three \texttt{YES} votes are \emph{useful} comments and the comments with no \texttt{YES} votes (i.e. three \texttt{NO} votes) are \emph{useless} comments. For the comments with one and two \texttt{YES} votes, we defined them as unclear comments.

@@

\begin{figure}[!t]
\centering
\includegraphics[scale=0.45, trim=0 0 30 50, clip=true]{scatter_log}
\caption{The similarity and distance plot of the training data.
The symbol represents the score, which ranges from 0 to 3.}
\label{fig:scatter}
\end{figure}

@@

To determine similarity and dissimilarity thresholds for useful and useless model, we iterated $s_t$ and $d_t$ values from every unique similarity and dissimilarity values in our data set.
%Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models, i.e. useful: $\Theta(c,S_T=0.015529,D_T=2.494944)$ and useless: $\Omega(c,S_T=0.087522,D_T=2.265679)$ on the samples.

\textbf{Model Effectiveness Results:} From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively. The precision and Recall of the models are 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model. We summarizes the number of classification from result described in Table \ref{tb:classify_number}.  We also show the results and relationship between comments class that manually classified and the similarity thresholds in Fig  \ref{fig:scatter}. The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} model. Thus, the comments drawn in the green area are those satisfied condition of useful model and the comments drawn in the red area are those satisfied condition of useless. While, the comments drawn in the white area are those not satisfied any condition (i.e. \emph{undetermined}). 
%This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.

%%Interpret: comments & model%%%%
As shown in the figure, most comments drawn in green area are useful and very few useless comments drawn in this area. Similarly, most comments in the red area are useless. The unclear comments are drawn in both area. Between these areas, there is an overlap section. This is because the similarity and dissimilarity values between useful and useless are vague. Both models tend to maximize coverage of classification. Thus, it is possible that there is overlap between these two models. However, from the results in Table \ref{tb:classify_number}, only three comments were classified overlap section. This shows that error of our models is low. Furthermore, there are 12 useless comments  (14\%) and  21 useful comments (17\%) still are undetermined (drawn in white area). We investigate characteristics of these comments. The findings are described in our discussion section.
%From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.

@@

%%Interpret: comments & similarity values%%%%
The graph also shows that the useful comments have less distance (not higher than 3 approximately) while most of useless comments have zero similarity. However, the unclear comments are still spread out over the graph which we cannot determine relationship between their similarity.
Furthermore, it is interesting that comments can be clearly separated into two major groups: comments with high similarity values and comment with zero similarity. This indicates that the comments  in each group have relationship other than similarity. This led us to investigate insight into these comments to find other properties in our future work.

Interestingly, in Table \ref{tb:classify_number}, there are 88\% of useful comments classified by our model have \texttt{YES} = 2 and 3 voting scores. The classification of useless comments also have similar proportion i.e. having high number of comment with \texttt{YES} = 0 and 1 voting scores. As the manual classification can be subjective, these comments were not received three voting scores.  It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments.

@@

\textbf{Validation:} We validated our approach using bootstrapping cross validation. We randomly selected 90\% of 318 comments for training set and determine thresholds. We then applied the constructed model on the remaining 10\% comments as the validation set.
The performance on the validation sets was measured using precision, recall and F-measure.
This validation was repeated for 300 times to estimate the performance of our models.
For a baseline of our models, we determined the performance of the random models using same methods.

Table \ref{tb:xvalidate} describes the performance of useful and useless classification models including an average and standard deviation of precision, recall, and F-measure. The results show that both of our models can achieve  60\% of precision and  75\% of recall approximately. Moreover, our models also achieved higher results than the random models twice for both precision and recall.

>>>>

\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignored all messages that automatically generated.
%In Gerrit, the comment history is composed of human-written comments from reviewers and automatically generated messages.
These automatic messages are generated by Gerrit, continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities. \textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'} are some examples. In practice, they are not considered in code review  and are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.

To do so, we first ignore all comments written by bots (i.e. \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}). Second, we removed message including reviewers comments by finding common patterns frequently occurred using regular expression. This would leave us only human-written comments that will be used in further preprocessing.

@@

\subsection{Manual Comment Usefulness Assessment}
In this case study, three participants (the first two authors and one student) independently classified comments by giving a question, ``does this comment technically contribute to its change or not?''
Then, the participants gave a vote for \texttt{YES} if the comment is likely to be useful and \texttt{NO} otherwise.
From the voting scores, we regarded that the comments with three \texttt{YES} votes are \emph{useful} comments and the comments with no \texttt{YES} votes (i.e. three \texttt{NO} votes) are \emph{useless} comments. For the comments with one and two \texttt{YES} votes, we defined them as unclear comments.

@@

\begin{figure}[!t]
\centering
\includegraphics[scale=0.45, trim=0 0 30 50, clip=true]{scatter_log}
\caption{The similarity and distance plot of the training data.
The symbol represents the score, which ranges from 0 to 3.
The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} model.}
\label{fig:scatter}
\end{figure}

@@

To determine similarity and dissimilarity thresholds for useful and useless model, we iterated $s_t$ and $d_t$ values from every unique similarity and dissimilarity values in our data set.
%Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models.
The selected models are $\Theta(c,S_T=0.015529,D_T=2.494944)$ for useful comments, and $\Omega(c,S'_T=0.087522,D'_T=2.265679)$ for useless comments.

\textbf{Model Effectiveness Results:} From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
The precision and recall of the models are 0.701 and 0.787 for useful model, and 0.648 and 0.824 for useless model.
We summarized the number of comments by manually-classified score and our classification result in Table \ref{tb:classify_number}.
The results and relationship between manual classification and our model based on similarity thresholds are shown in Fig  \ref{fig:scatter}.
Comments in the green area are those that satisfied the conditions of the useful model.
Comments in the red area are those that satisfied condition of the useless model.
Finally, comments in the white area are those that did not satisfy any condition (i.e. \emph{undetermined}). 
%This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.

%%Interpret: comments & model%%%%
As shown in the figure, most useful comments went into the green area; only few useful comments ended up in the red area.
Similarly, most useless comments went into the red area.
The unclear comments are drawn in both area.
Between these areas, there is an overlap section.
This is because the similarity and dissimilarity values between useful and useless are vague.
Both models tried to maximize the coverage (and the precision) of classification, which makes it possible that there is some overlapping between these two models.
Fortunately, this overlapping area is small.

% These should go into the discussion.
%However, from the results in Table \ref{tb:classify_number}, only three comments were classified in the overlapping section.
%This shows that error of our models is low. Furthermore, there are 12 useless comments  (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area). We investigate characteristics of these comments. The findings are described in our discussion section.
%From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.

@@

%%Interpret: comments & similarity values%%%%
The graph also shows that the useful comments have low dissimilarity value (less than 3, approximately),
while most useless comments have zero similarity.
However, the unclear comments are spread out over the graph in a way which we cannot classify using our model.
This suggests that other factors may come into play.

%Interestingly, comments can be clearly separated into two major groups: comments with high similarity values and comment with zero similarity. This indicates that the comments  in each group have relationship other than similarity. This led us to investigate insight into these comments to find other properties in our future work.

Interestingly, in Table \ref{tb:classify_number},
89\% of useful-class comments received 2 or 3 \texttt{YES} votes,
and 88\% of useless-class comments received 0 or 1 \texttt{YES} votes.

%Probably should be in the discussion?
% As manual classification can be subjective, these comments were not received three voting scores.
% It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments.

@@

\textbf{Validation:}
We validated our approach using bootstrapping cross validation.
We randomly selected 90\% of 318 comments for training set and determine thresholds.
The constructed model is then applied on the remaining 10\% comments as the validation set.
The precision, recall and F-measure scores are measured and recorded.
This validation was repeated 300 times to give an average performance of our models.
For a baseline, we also determined the performance of the random classifier using the same methods.

Table \ref{tb:xvalidate} describes the performance of useful and useless classification models including an average and standard deviation of precision, recall, and F-measure.
The results show that both of our models can achieve 60\% of precision and 75\% of recall, approximately.
In addition, our models also achieved higher results than the random models twice for both precision and recall.
